VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-24 snapshot_system/paper_analysis.tex
added VO+ approach to explain why we can't rely on DFS features for extra replication

Now we  assess  the impact of losing $d$ machines 
to the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use an FSB rather than a deduplication
data chunk as our unit of failure because the DFS keeps
file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probability of losing a snapshot FSB of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
if this block is used by the VM.

>>>>

Now we  assess  the impact of losing $d$ machines 
to the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
%We use an FSB rather than a deduplication
%data chunk as our unit of failure because the DFS keeps
%file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probability of losing a snapshot FSB of a VM by
estimating the number of file system blocks per VM in each approach.
%As illustrated in Figure~\ref{fig:share},
%we build a bipartite graph representing the association from unique file system blocks
%to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
%if this block is used by the VM.

As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
association from unique file system blocks to their corresponding VMs in the VC
and VO approaches. We use an FSB rather than data chunk as our unit of failure
because the DFS keeps file system blocks as its base unit of storage, and in
the case of 64MB FSBs and 4KB chunks, there are 16K chunks per block. In VC
we assign extra replication to the PDS blocks, while in VO the replication
degree is fixed.

We could consider a third approach (call it VO+), adopting the VO approach, and
then relying on filesystem features to provide extra replication to popular
blocks, without the extra complexity of separating popular and non-popular
data. The problem with this VO+ approach is that without separating the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system. Because the popular blocks
are dispersed, there are very few popular FSBs. The end result is that we
either have to add extra replication on unpopular chunks to ensure the popular
chunks have sufficient replication, or we have to accept a reduced replication
factor on popular chunks. This explains why we must separate the PDS and
non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both
can be stored on the same DFS).
